---
title: "Data Cleaning Process"
format:
  html:
    code-fold: true
    tbl-cap-location: top
---

## Standard Cleaning Procedures

### 1. Initial Data Assessment
- Review data completeness and quality metrics
- Generate summary statistics for all variables
- Identify missing or incomplete records
- Flag potential data quality issues
- Document initial state of dataset

### 2. Automated Cleaning Steps
1. **Standardization**
   - Convert all dates to YYYY-MM-DD format
   - Standardize text case (upper/lower) as appropriate
   - Normalize units of measurement
   - Apply consistent coding schemes

2. **Missing Data Handling**
   - Flag missing values
   - Assess patterns of missingness
   - Apply appropriate imputation where valid
   - Document all missing data decisions

3. **Outlier Detection**
   - Calculate statistical bounds for numeric variables
   - Flag biological impossibilities
   - Review extreme values
   - Document outlier handling decisions

4. **Deduplication**
   - Identify potential duplicate records
   - Compare record pairs
   - Merge or remove duplicates
   - Maintain audit trail of changes

### 3. Manual Review Process
1. **Expert Review**
   - Clinical review of flagged values
   - Assessment of unusual patterns
   - Validation of automated decisions
   - Documentation of override reasons

2. **Quality Checks**
   - Cross-reference with source data
   - Verify referential integrity
   - Validate derived variables
   - Check logical consistency

### 4. Documentation Requirements
Each cleaning step must include:

- Description of issue addressed
- Methodology used
- Number of records affected
- Before/after comparisons
- Justification for changes
- SQL or code snippets used
- Reviewer sign-off

### 5. Validation Steps
1. **Technical Validation**
   - Run automated test suites
   - Verify data types and formats
   - Check constraint compliance
   - Validate calculations

2. **Clinical Validation**
   - Review by subject matter experts
   - Check clinical plausibility
   - Verify coding accuracy
   - Validate derived measures

### 6. Final Quality Control
- Generate final quality metrics
- Produce validation reports
- Document all cleaning steps
- Archive original and cleaned datasets
- Create reproducible cleaning workflow

### 7. Ongoing Maintenance
- Regular quality monitoring
- Periodic data audits
- Update cleaning procedures
- Maintain cleaning documentation
- Track data quality metrics

### Quality Standards
All cleaned data must meet:

- 99.9% completeness for required fields
- 100% referential integrity
- No invalid codes or values
- Full documentation of changes
- Reproducible cleaning process

### Tools and Resources
- Custom SQL cleaning scripts
- Statistical analysis software
- Data validation tools
- Documentation templates
- Quality control checklists


## Data Files Overview
### Data Dictionary

The dataset contains several key variable categories:

1. **Diagnosis Variables**
   - Includes diagnosis codes, dates, severity
   - Links to visits through visit_id
   - Tracks chronic conditions and resolution

2. **Medication Variables** 
   - Prescription details and status
   - Dosage, frequency, dates
   - Pharmacy and prescriber tracking

3. **Lab Results**
   - Test results with reference ranges
   - Collection and result dates
   - Abnormality flagging

4. **Vital Signs**
   - Standard clinical measurements
   - Height, weight, BMI
   - Cardiovascular and respiratory metrics

See the full data dictionary for detailed variable specifications.



```{r}
#| label: setup
#| include: false
library(tidyverse)
library(duckdb)
library(data.table)
library(arrow)
library(reactable)

rootdir <- "/home/rstudio/SALUS/_Inbox/01_Preprocessing/A01_ë°ì´í„°ì •ë¦¬/"

took <- function(expr) {
  start_time <- Sys.time()
  result <- expr
  end_time <- Sys.time()
  execution_time <- difftime(end_time, start_time, units = "secs")
  print(paste("Execution time:", round(execution_time, 2), "seconds"))
  return(result)
}

f_size <- function(x) {
  x %>% object.size() %>% format(units = "MB")
}
```

:::{.callout-note}
## File Categories
- **AINQ**: Inquiry data files
- **RSLT**: Results data files
- **JUDD**: Judgment data files
:::

```{r}
#| label: file-listing
#| tbl-cap: "SALUS Data Files Overview"
#| column: page

list_files <- list()

list_files$CSV <- lapply(
  c("AINQ", "RSLT", "JUDD"),
  function(dir) {
    list.files(
      file.path(rootdir, "data/processed/encoding/UTF-8_unix/csv", dir),
      recursive = TRUE,
      full.names = TRUE
    )
  }
) %>% setNames(c("ainq", "rslt", "judd"))

list_tables <- function(name) {
  dbpath <- sprintf(rootdir,"data/processed/_objects/_duckdb/%s.duckdb", name)
  dbconn <- dbConnect(duckdb(), dbpath)
  cat("ðŸ“Œ", name, "tables:")
  tables <- dbconn %>% dbListTables()
  dbDisconnect(dbconn, shutdown = TRUE)
  return(tables)
}
library(stringr)

list_files$CSV$SET <- Map(
  function(ainq_file, rslt_file, judd_file) {
    c(ainq_file, rslt_file, judd_file)
  },
  list_files$CSV$ainq,
  list_files$CSV$rslt, 
  list_files$CSV$judd
) %>% setNames(
  basename(list_files$CSV$ainq) %>% 
    str_remove("AINQ_") %>%
    str_remove("\\.csv$")
)

print("ðŸ“Œ Created", length(list_files$CSV$SET), "file sets\n")
reactable(
  data.frame(
    Year = str_extract(names(list_files$CSV$SET), "^\\d{4}"),
    InstCode = str_extract(names(list_files$CSV$SET), "\\d{3}$"),
    AINQ = basename(sapply(list_files$CSV$SET, `[`, 1)),
    RSLT = basename(sapply(list_files$CSV$SET, `[`, 2)), 
    JUDD = basename(sapply(list_files$CSV$SET, `[`, 3))
  ),
  defaultPageSize = 10,
  striped = TRUE,
  bordered = TRUE,
  searchable = TRUE,
  showPageSizeOptions = TRUE,
  pageSizeOptions = c(10, 20, 50),
  defaultColDef = colDef(
    align = "left",
    minWidth = 120
  ),
  columns = list(
    Year = colDef(
      name = "Year",
      style = list(fontWeight = "bold"),
      sortable = TRUE
    ),
    InstCode = colDef(
      name = "Institution Code",
      style = list(fontWeight = "bold"),
      sortable = TRUE
    ),
    AINQ = colDef(
      name = "AINQ File",
      minWidth = 200
    ),
    RSLT = colDef(
      name = "RSLT File", 
      minWidth = 200
    ),
    JUDD = colDef(
      name = "JUDD File",
      minWidth = 200
    )
  ),
  theme = reactableTheme(
    borderColor = "#dfe2e5",
    stripedColor = "#f6f8fa",
    headerStyle = list(
      backgroundColor = "#f8f9fa",
      fontWeight = "bold"
    )
  ),
  defaultSorted = list(
    Year = "desc",
    InstCode = "asc"
  )
)


```

