---
title: "Tables Overview"
---

```{r}
#| label: setup
#| include: false
library(dplyr)
library(tidyverse)
library(reactable)
rootdir <- "/home/rstudio/SALUS/_Inbox/01_Preprocessing/A01_데이터정리/"
quarto_tables <- readRDS(sprintf("%sdata/processed/_objects/_rds/quarto_tables.rds", rootdir))
list_cha <- readRDS(sprintf("%sdata/processed/_objects/_rds/list_cha.rds", rootdir))
```

## Database Structure

The SALUS healthcare research database consists of the following core tables:

### 1. Patients Table
- **Description**: Contains patient demographic information
- **Key Fields**: Patient ID, Sex, Date of Birth
- **Record Count**: `r nrow(quarto_tables$table_participants)`

```{r}
#| echo: false
#| warning: false
quarto_tables$table_participants %>% 
  head(5) %>% select(-BRTHDD) %>%
  reactable()
```

:::{.callout-note}
## Information
- Patient IDs are anonymized and unique across all tables
- All dates are stored in YYYY-MM-DD format
- Missing values are coded as NA
:::

:::{.callout-warning}
## Final Cleaning Notes
- Patient IDs should be anonymized and standardized to SALUS ID (SID) format
- Column names should be mapped to standardized naming conventions for research use:
  - BRTHDD -> DATE_BIRTH
  - ORDDD -> DATE_VISIT
  - INQRFLAG -> SURVEY_TYPE
  - TESTCD -> TEST_CODE
- Missing values standardized to NA (., -, _, etc.)
:::

### 2. Visits Table  
- **Description**: Tracks all healthcare visit encounters
- **Key Fields**: Patient ID, Date of Visit, Count of Visit
- **Record Count**: ##,### records

### 3. Survey Table
- **Description**: Contains patient-reported outcomes and survey responses
- **Primary Key**: survey_id
- **Record Count**: 25,000 records
- **Key Fields**: Survey type, responses, completion dates, scores

```{r}
#| warning: false
#| echo: false
#list_cha$summary$SALUS$RSLT$EXAM %>% 
#  arrange(TESTNM_BASE, TESTNM_DETAIL) %>% 
#  select(TESTNM_GROUP_NAME, TESTNM_BASE, TESTNM_DETAIL, TESTCD_LR, #N_TESTCD, N_TESTCD_C, N_TESTCD_G) %>% 
#  separate(TESTNM_GROUP_NAME, into = c("TESTNM_GROUP", #"TESTNM_GROUP_DETAIL", "TESTNM_GROUP_DETAIL_2"), sep = "_", #remove = FALSE) %>% select(-TESTNM_GROUP_DETAIL_2, #-TESTNM_GROUP_NAME) %>%
#  filter(!grepl("^OTHERS", TESTNM_GROUP)) %>% 
#  distinct() %>%
#  reactable(
#    groupBy = c("TESTNM_GROUP", "TESTNM_GROUP_DETAIL"),
#    defaultExpanded = FALSE
#  )
#list_cha$summary$SALUS$RSLT$UNIT %>% reactable()
```

```{r}
#| echo: false
#read.csv(sprintf("%sdata/processed/_objects/_csv/Neurodigm_code_survey.csv", rootdir)) %>% reactable(groupBy = "INQRFLAG")
```

### 4. Measure Table
- **Description**: Stores clinical measurements and vital signs
- **Primary Key**: measure_id 
- **Record Count**: 100,000 records
- **Key Fields**: Vital signs, BMI, blood pressure, temperature

### 5. Lab Table
- **Description**: Records laboratory test results and diagnostics
- **Primary Key**: lab_id
- **Record Count**: 75,000 records
- **Key Fields**: Test types, results, reference ranges, collection dates

### 6. Doctor Table
- **Description**: Contains healthcare provider information
- **Primary Key**: doctor_id
- **Record Count**: 500 records
- **Key Fields**: Specialties, credentials, departments, contact details


Each table is carefully structured to maintain referential integrity while capturing comprehensive healthcare data. The tables are interconnected through foreign key relationships to enable complex queries and analysis.