---
title: "Tables Overview"
---

```{r}
#| label: setup
#| include: false
library(dplyr)
library(reactable)
rootdir <- "/home/rstudio/SALUS/_Inbox/01_Preprocessing/A01_데이터정리/"
quarto_tables <- readRDS(sprintf("%sdata/processed/_objects/_rds/quarto_tables.rds", rootdir))
```

## Database Structure

The SALUS healthcare research database consists of the following core tables:

### 1. Patients Table
- **Description**: Contains patient demographic information
- **Key Fields**: Patient ID, Sex, Date of Birth
- **Record Count**: `r nrow(quarto_tables$table_participants)`

```{r}
quarto_tables$table_participants %>% 
  head(5) %>% select(-BRTHDD) %>%
  reactable()
```

### 2. Visits Table  
- **Description**: Tracks all healthcare visit encounters
- **Key Fields**: Patient ID, Date of Visit, Count of Visit
- **Record Count**: ##,### records

### 3. Survey Table
- **Description**: Contains patient-reported outcomes and survey responses
- **Primary Key**: survey_id
- **Record Count**: 25,000 records
- **Key Fields**: Survey type, responses, completion dates, scores

### 4. Measure Table
- **Description**: Stores clinical measurements and vital signs
- **Primary Key**: measure_id 
- **Record Count**: 100,000 records
- **Key Fields**: Vital signs, BMI, blood pressure, temperature

### 5. Lab Table
- **Description**: Records laboratory test results and diagnostics
- **Primary Key**: lab_id
- **Record Count**: 75,000 records
- **Key Fields**: Test types, results, reference ranges, collection dates

### 6. Doctor Table
- **Description**: Contains healthcare provider information
- **Primary Key**: doctor_id
- **Record Count**: 500 records
- **Key Fields**: Specialties, credentials, departments, contact details


Each table is carefully structured to maintain referential integrity while capturing comprehensive healthcare data. The tables are interconnected through foreign key relationships to enable complex queries and analysis.